The Genetic Algorithm of GMSE

### 2018-05-24 notebook/ms/SI1.Rmd

---
title: 'The Genetic Algorithm of GMSE'
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting Information 1)'
author: A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;,
  Jeroen Minderman&#xb9;, Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, 
  O. Sarobidy Rakotonarivo&#xb9;, Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: "[1] Biological and Environmental Sciences, University of Stirling, Stirling, UK
[2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
linestretch: 1
bibliography: gmse.bib
biblio-style: apalike
link-citations: true
linkcolor: blue
---

@@

Following crossover, `POPULATION` array elements affecting agent actions (columns 8-13) mutate at a fixed probability of `ga_mutation`. For each array element, a random uniform number $u \in [0, 1]$ is sampled. If $u$ is greater than `1 - (0.5 * ga_mutation)`, then the value of the array element is increased by 1. If $u$ is less than `0.5 * ga_mutation`, then the value of the array element is decreased by 1; when this decrease results in a negative value, the mutated value is multiplied by -1 to equal 1.

>>>>

---
title: 'The Genetic Algorithm of GMSE'
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting Information 1)'
author: A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;,
  Jeroen Minderman&#xb9;, Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, 
  O. Sarobidy Rakotonarivo&#xb9;, Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: "[1] Biological and Environmental Sciences, University of Stirling, Stirling, UK
[2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
bibliography: gmse.bib
biblio-style: apalike
link-citations: true
linkcolor: blue
---

@@

Following crossover, `POPULATION` array elements affecting agent actions (columns 8-13) mutate at a fixed probability of `ga_mutation`. For each array element, a random uniform number $u \in [0, 1]$ is sampled. If $u$ is greater than `1 - (0.5 * ga_mutation)`, then the value of the array element is increased by 1. If $u$ is less than `0.5 * ga_mutation`, then the value of the array element is decreased by 1; when this decrease results in a negative value, the mutated value is multiplied by -1 to be positive.
